\section*{\fontsize{18pt}{1}\selectfont Timetable}

The schedule is broken into 15 2-week periods, with the first period starting on 19/10/2018.

\begin{enumerate}
	%1
	\item \textbf{Michaelmas weeks 2--4 [19/10--5/11]:} Preparatory reading on the P4 programming language and setting up the NetFPGA platform. Going through the tutorials and experimenting with some examples. Study TCP congestion control and recovery mechanisms beyond the material taught in \emph{Computer Networking} and \emph{Principles of Communications} courses.
	
	%2
	\item \textbf{Michaelmas weeks 5--6 [6/11--19/11]:} Design the architecture: mapping the application to a match-action pipeline.
	\\
	\textbf{\underline{Milestone:} Understand the application architecture. Be able to map the application to a match-action pipeline.}
	
	%3
	\item \textbf{Michaelmas weeks 7--8 [20/11--28/11]:} Start implementing of the design by writing the basic code. 
	
	%4
	\item \textbf{Michaelmas vacation weeks 1--2 [30/11--12/12]:} Simulate the application using bmv2/Xilinx simulators. 
	\\
	\textbf{\underline{Milestone:} Basic design written in P4 working in simulation, with minimal bugs left.} .
	
	%5
	\item \textbf{Michaelmas vacation weeks 3--4 [13/12--26/12]:} Start to implement the working code into hardware. Write a hardware-test program (Python-based). 
	
	%6
	\item \textbf{Michaelmas vacation weeks 5--7 [27/12--16/1]:} Demonstrate interoperability with a software-based client/application. Start writing the progress report.
	\\
	\textbf{\underline{Milestone:} Have the application working in hardware, a completed progress report and a presentation for demonstration purposes.}
	
	%7
	\item \textbf{Lent weeks 1--2 [17/1--30/1]:} Work on the design's performance testing and evaluation.
	
	%8
	\item \textbf{Lent weeks 3--4 [31/1--13/2]:} Continue working on testing and evaluation of the design.
	\\
	\textbf{\underline{Milestone:} The project is finished and meets the success criteria.}
	
	%9
	\item \textbf{Lent weeks 5--6 [14/2--27/2]:} Start working on extensions, based on project's progress.
	\\
	\textbf{\underline{Milestone:} The prototype continues to work well with the extensions implemented.}
	
	%10
	\item \textbf{Lent weeks 7--8 [28/2--13/3]:} Possible overflow from the previous weeks. Clean up codes and repository. Start writing dissertation main chapters.
	\\
	\textbf{\underline{Milestone:} Completed working prototype with core components and extensions in place. First draft of dissertation}
	
	%11
	%12	
	%13
	\item \textbf{Easter vacation:} Continue writing dissertation. Review cycles and corrections to dissertation towards the end of the vacation.
	
	%14
	\item \textbf{Easter weeks 1--2 [25/4--8/5]:}  Completed dissertation. Proof reading and then an early submission so as to concentrate on examination revision.
	
	%15
	\item \textbf{Easter weeks 3 [9/5--17/5]:} Buffer week.
\end{enumerate}